Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-16 ms.tex
stripe vs window from AZlab

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
\caption{
Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
}\label{fig:crosshatchModelGallery}
\end{figure}

@@

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{psd_models_gallery.pdf}
\caption{
Best-fit power spectra of all the NIRCam detectors show that the long wavelength detectors A5 and B5 show the most pronounced crosshatch patterns.
The primary crosshatch tends to be aligned closely, but no exactly, with either the X or Y axis.
The images have all been normalized to the same scale to show the relative crosshatch amplitudes of different detectors.
}\label{fig:crosshatchModelGallery}
\end{figure}

@@

\subsubsection{Stripe versus Window Mode}
\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:persistence}
\end{figure*}
